Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Pseudo-anonymity @naszam

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways:
\newline 1. via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent;
\newline 2. via private transactions allowed by AZTEC Protocol security layer via zkANTS. Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.

EOA in Ethereum are controlled by private key. An user can send messages from an externally owned account by creating and signing a transaction. The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
\newline To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol. In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-ZK Rollup by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

>>>>

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol security layer via zkANTS.

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol. In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-ZK Rollup by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
